\documentclass[a4paper,10pt]{article}

% ---------- PAGE SETUP ----------
\usepackage[a4paper, top=0.25in, bottom=0.25in, left=0.45in, right=0.45in]{geometry}
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\raggedright

% ---------- FONT ----------
\setmainfont{Noto Sans}

% ---------- COLORS ----------
\definecolor{msblue}{RGB}{0,70,140}

% ---------- SECTION STYLE ----------
\titleformat{\section}
  {\large\bfseries\color{msblue}\uppercase}
  {}
  {0pt}
  {}
  [\vspace{-3pt}\titlerule]

\titlespacing*{\section}{0pt}{4pt}{3pt}

% ---------- LISTS ----------
\setlist[itemize]{
  leftmargin=0.15in,
  itemsep=1pt,
  topsep=2pt,
  parsep=0pt
}
\renewcommand\labelitemi{\tiny$\bullet$}

% ---------- COMMANDS ----------
\newcommand{\resumeEntry}[4]{
  \textbf{#1} \hfill #2\\
  \textit{#3} \hfill \textit{#4}
}
\newcommand{\projectEntry}[3]{
  \noindent\textbf{#1} $|$ \textit{#2} \hfill #3
}

\begin{document}

% ================= HEADER =================
\begin{center}
  {\LARGE \textbf{MUHAMMED AJMAL U K}}\\[4pt]
  \small
  \href{mailto:ajmaluk.me@gmail.com}{ajmaluk.me@gmail.com} $|$
  +91 85471 97122 $|$
  \href{https://linkedin.com/in/ajmal-uk}{linkedin.com/in/ajmal-uk} $|$
  \href{https://github.com/ajmal-uk}{github.com/ajmal-uk} $|$
  \href{https://ajmaluk.netlify.app}{ajmaluk.netlify.app}
\end{center}

\vspace{-4pt}

% ================= SUMMARY =================
\section{Professional Summary}
Software Engineering Intern candidate and MCA student with a strong foundation in
\textbf{computer science fundamentals, data structures, and algorithms}.
Hands-on experience designing, developing, and testing scalable web and mobile
applications using Python, Flutter, Flask, SQL, and Firebase. Built production
systems generating \textbf{10K+ organic clicks} and AI-powered solutions focused
on performance, reliability, and user impact. Thrives in collaborative environments
with a growth mindset and passion for learning new technologies.

% ================= SKILLS =================
\section{Technical Skills}
\begin{itemize}
  \item \textbf{Programming Languages:} Python, Dart, JavaScript, SQL
  \item \textbf{Frameworks \& Libraries:} Flutter, Flask, React.js (basic), Tailwind CSS
  \item \textbf{Databases:} MySQL, Firebase Realtime DB, Firestore
  \item \textbf{Cloud \& Tools:} Git, GitHub, Firebase, PythonAnywhere, Netlify, Postman
  \item \textbf{AI \& Systems:} LLM Integration, Chatbot Development, Gemini API
  \item \textbf{CS Fundamentals:} Data Structures, Algorithms, OOP, State Management
\end{itemize}

% ================= PROJECTS =================
\section{Projects}

\projectEntry{Dementia Virtual Memory Assistant}{Flutter, Python, Flask}{Aug 2025 -- Oct 2025}
\begin{itemize}
  \item Designed and developed a mobile application to support dementia patients
  with reminders, memory logs, and caregiver coordination.
  \item Implemented real-time facial recognition using \textbf{DeepFace (ArcFace)}
  via Flask to identify family members and improve user safety.
  \item Applied clean architecture principles to ensure maintainability and scalability.
\end{itemize}

\projectEntry{ToolPix — AI Tools Platform}{Flask, SQL, Gemini API}{Apr 2025 -- Jun 2025}
\begin{itemize}
  \item Built a scalable web platform offering developer utilities and AI automation tools.
  \item Improved performance and availability through query optimization and backend tuning.
  \item Achieved \textbf{10K+ organic clicks} using SEO best practices and AI-driven content generation.
\end{itemize}

\projectEntry{Byte AI — Multi-Model Chatbot}{Python, Flask, LLM APIs}{Mar 2024 -- Sep 2024}
\begin{itemize}
  \item Developed a multi-model chatbot integrating \textbf{Gemini, Groq, and OpenRouter}.
  \item Designed a clean ChatGPT-style UI and modular backend routing for extensibility.
\end{itemize}

\projectEntry{Explore Together — Travel Matching App}{Flutter, Firebase}{Oct 2024 -- Dec 2024}
\begin{itemize}
  \item Built a real-time travel matching application connecting users based on destinations.
  \item Implemented live updates and messaging using Firebase services.
\end{itemize}

% ================= EXPERIENCE =================
\section{Experience}

\resumeEntry{Full Stack Web Development Intern}{Nov 2025 -- Dec 2025}{Future Interns}{Remote}
\begin{itemize}
  \item Collaborated with team members to build and improve web features using React and Tailwind.
  \item Applied Git-based workflows and incorporated feedback to enhance code quality.
\end{itemize}

\resumeEntry{Data Analytics Virtual Experience}{Nov 2025}{Deloitte Australia (Forage)}{Remote}
\begin{itemize}
  \item Analyzed datasets to identify trends and support data-driven decisions.
  \item Built Tableau dashboards to communicate insights to stakeholders.
\end{itemize}

% ================= EDUCATION =================
\section{Education}

\textbf{Master of Computer Applications (MCA)} \hfill 2025 -- 2027\\
College of Engineering, Trivandrum

\vspace{1pt}

\textbf{B.Sc. Computer Science} \hfill 2022 -- 2025\\
Mahatma Gandhi College, Iritty \hfill \textbf{CGPA: 8.97}

% ================= CERTIFICATIONS =================
\section{Certifications \& Leadership}
\begin{itemize}
  \item IBM Software Engineering — Coursera
  \item Oracle OCI AI Foundations Associate
  \item Oracle AI Agent Studio Foundations
  \item Google \& Kaggle AI Agent Development Program
  \item NCC Sergeant — B \& C Certificates
  \item Co-manages a YouTube channel with \textbf{500K+ subscribers}
\end{itemize}

\end{document}
