\documentclass[a4paper,10pt]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, top=0.25in, bottom=0.25in, left=0.45in, right=0.45in]{geometry}
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\raggedright

% Font
\setmainfont{Noto Sans}

% Colors
\definecolor{darkblue}{RGB}{0,70,140}

% Section Formatting
\titleformat{\section}
  {\large\bfseries\color{darkblue}\uppercase}
  {}
  {0pt}
  {}
  [\vspace{-3pt}\titlerule]

\titlespacing*{\section}{0pt}{4pt}{3pt}

% List Formatting
\setlist[itemize]{
  leftmargin=0.15in,
  labelsep=4pt,
  itemsep=0pt,
  parsep=0pt,
  topsep=2pt
}

\renewcommand\labelitemi{\tiny$\bullet$}

% Commands
\newcommand{\resumeEntry}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4}
}

\newcommand{\projectEntry}[3]{
  \noindent\textbf{#1} $|$ \textit{#2} \hfill #3
}

\begin{document}

% HEADER
\vspace{8pt}
\begin{center}
    {\LARGE \textbf{MUHAMMED AJMAL U K}} \\[4pt]
    \small
    \href{mailto:ajmaluk.me@gmail.com}{ajmaluk.me@gmail.com} $|$
    +91 85471 97122 $|$
    \href{https://linkedin.com/in/ajmal-uk}{linkedin.com/in/ajmal-uk} $|$
    \href{https://github.com/ajmal-uk}{github.com/ajmal-uk} $|$
    \href{https://ajmaluk.netlify.app}{ajmaluk.netlify.app}
\end{center}

\vspace{-4pt}

% SUMMARY
\section{Professional Summary}
Full-stack developer and MCA student with hands-on experience building mobile and web applications using Python, Flutter, Firebase, SQL, and Flask. Delivered production-ready projects generating 10K+ organic clicks through AI-driven SEO and developed AI chatbots, automation tools, and real-time safety solutions. Strong in debugging, problem-solving, and rapid learning, with a focus on clean architecture, scalability, and efficient engineering practices.

% SKILLS
\section{Technical Skills}
\begin{itemize}
    \item \textbf{Programming:} Python, Dart, JavaScript, SQL
    \item \textbf{Frameworks \& Tools:} Flutter, Flask, React.js (basic), Tailwind CSS
    \item \textbf{Databases:} MySQL, Firebase Realtime DB, Firestore
    \item \textbf{Development Tools:} Git, GitHub, VS Code, Postman, Android Studio
    \item \textbf{Cloud \& Deployment:} Firebase, PythonAnywhere, Netlify, Cloudinary, OneSignal
    \item \textbf{AI Skills:} Prompt Engineering, LLM Integration, AI Fundamentals, Chatbot Development
    \item \textbf{Core Concepts:} Data Structures, Algorithms, OOP, State Management
    \item \textbf{Soft Skills:} Leadership, Teamwork, Communication, Project Management, Fast Learning
\end{itemize}

% PROJECTS
\section{Projects}

% Dementia App
\projectEntry{Dementia Virtual Memory Assistant}{Flutter, Python, DeepFace}{Aug 2025 -- Oct 2025}
\begin{itemize}
    \item Developed a caregiver–patient support app with task management, reminders, diary, and personal memory gallery.
    \item Integrated DeepFace (ArcFace) in a Flask backend to identify family members from quick photo scans.
    \item Repo: \href{https://github.com/ajmal-uk/dementia-virtual-memory}{github.com/ajmal-uk/dementia-virtual-memory}
\end{itemize}

% ToolPix
\projectEntry{ToolPix — AI Tools Platform}{Flask, Gemini API, AI SEO}{Apr 2025 -- Jun 2025}
\begin{itemize}
    \item Built AI tool platform featuring developer utilities and compilers.
    \item Achieved \textbf{10K+ organic clicks} through strong SEO.
    \item Live: \href{https://toolpix.pythonanywhere.com}{toolpix.pythonanywhere.com}
\end{itemize}

% Explore Together
\projectEntry{Explore Together — Travel Buddy Finder}{Flutter, Firebase}{Oct 2024 -- Dec 2024}
\begin{itemize}
    \item Developed a travel buddy–matching system that pairs users with similar trip destinations.
    \item Implemented real-time trip updates and chat-ready matching for smoother coordination.
    \item Built as an academic project for the B.Sc. Computer Science program at Mahatma Gandhi College.
    \item Repo: \href{https://github.com/ajmal-uk/explore-together}{github.com/ajmal-uk/explore-together}
\end{itemize}

% Byte AI
\projectEntry{Byte AI — Multi-Model Chatbot}{Python, Flask, Gemini API}{Mar 2024 -- Sep 2024}
\begin{itemize}
    \item Built chatbot supporting Gemini, Groq, and OpenRouter LLMs.
    \item Clean ChatGPT-style UI using HTML/CSS/JS.
    \item Live: \href{https://byteai.pythonanywhere.com}{byteai.pythonanywhere.com}
\end{itemize}

% EXPERIENCE
\section{Virtual Experience}

\resumeEntry{Full Stack Web Development Intern}{Nov 2025 -- Dec 2025}{Future Interns}{Remote}
\begin{itemize}
    \item Built modular React.js + Tailwind components and improved UI responsiveness through iterative redesigns.
    \item Followed clean Git workflows with structured commits, delivering all assigned tasks on time.
\end{itemize}

\resumeEntry{Deloitte Australia — Data Analytics Simulation}{Nov 2025}{Forage}{Remote}
\begin{itemize}
    \item Completed Deloitte’s analytics simulation involving data cleaning, Excel classification, and insight generation.
    \item Created a Tableau dashboard to visualize trends and support data-driven decision making.
\end{itemize}

% EDUCATION
\section{Education}

\textbf{Master of Computer Applications (MCA)} \hfill 2025 -- 2027 \\
College of Engineering, Trivandrum

\vspace{1pt}

\textbf{B.Sc. Computer Science} \hfill 2022 -- 2025 \\
Mahatma Gandhi College, Iritty \hfill CGPA: 8.97

% CERTIFICATIONS
\section{Certifications \& Leadership}
\begin{itemize}
    \item IBM Software Engineering (Coursera)
    \item Google \& Kaggle AI Agent Development (5-Day)
    \item Google Cloud Arcade Facilitator (Milestone 3)
    \item Oracle OCI AI Foundations Associate
    \item Oracle AI Agent Studio Foundations
    \item NCC Sergeant (B \& C Certificates)
    \item Co-manages YouTube gaming channel with \textbf{500K+ subscribers}
\end{itemize}

\end{document}
